API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
@ogrisel's affiliation

\institute{University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Nuxeo \and 
           University of Bucharest \and
           Bauhaus-Universitat \and
           Telecom ParisTech \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}

>>>>

\institute{Informatics Institute, University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Independent consultant \and
           University of Bucharest \and
           Ciuvo GmbH \and
           Telecom ParisTech \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}
